Performing Cluster Analysis on TAD boundaries & Annotations

### 2019-04-05 Scripts/evaluating_pca.Rmd
editted pca script

## Saving clustered annotation plots

@@

###GM12878

@@

###K562

@@

# Clustering TADs

>>>>

## Clustering annotations

@@

###Saving clustering annotations plots

@@

####K562

@@

## Clustering annotations (unseparated)

```{r}
pcaplotfunction <- function(cl, resolution){

  if(cl=="GM12878"){
    countdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", resolution, "_count.rds",
                    sep="")
    percdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", resolution, "_perc.rds",
                    sep="")
    distdir = paste("Z:/TAD_data_analysis/", cl, "/", resolution, "/Ensemble/PCA/pcadat_gm12878_", resolution, "_dist.rds",
                    sep="")
  }else{
      countdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_count.rds",
                    sep="")
    percdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_perc.rds",
                    sep="")
    distdir = paste("Z:/TAD_data_analysis/K562/", resolution, "/Ensemble/PCA/pcadat_K562_dist.rds",
                    sep="")
    }

  countdata <- readRDS(countdir)
  percdata <- readRDS(percdir)
  distdata <- readRDS(distdir)

  #performing log2 transformation on distances
  distdata <- apply(distdata,2,function(x){log(x + 1, base=2)})

  data <- (countdata + percdata + distdata)/3

  colnames(data) <- gsub(paste(c("Gm12878", "K562",
                                 "-",
                                 "_",
                                 "Haib",
                                 "Sydh",
                                 "Uta",
                                 "Uw",
                                 "Broad",
                                 "Uchicago",
                                 "count",
                                 "perc",
                                 "dist"), collapse = "|"),"", colnames(data))

## Clustering TADs
